---
title: "susieR::susie_rss Optimation"
author: "Yunshen Bai"
date: "`r Sys.Date()`"
output: html_document
---

The `susieR` package introduces a simple approach for conducting variable selection in multiple regression. The methods implemented here are particularly well-suited to settings where some of the X variables are highly correlated, and the true effects are highly sparse. `susie_rss` performs variable selection under a sparse Bayesian multiple linear regression of Y on X using the z-scores from standard univariate regression of Y on each column of X. In this report, we will perform the line profiling to find the most time and memory consuming part and try to optimize it.

This is the data set we will use in this report.
```{r}
setwd("D:/Jupyter_notebook/susie_rss")
ss_qc=read.csv("D:/Jupyter_notebook/susie_rss/ss_qc.csv",header = T)
LD=read.csv("D:/Jupyter_notebook/susie_rss/LD.csv",header = F)
```

Then, we perform the line profiling to find out the part that spend most of memory and time. 

```{r,warning=FALSE}
library(profvis)
p=profvis({
  susieR:::susie_rss(as.matrix(ss_qc$z),as.matrix(LD), n = 1138870,var_y, z_ld_weight = 0, estimate_residual_variance = FALSE, 
            prior_variance = 50, check_prior = TRUE, max_iter = 1000,verbose = TRUE )
})
p

```
```{r,include=FALSE}
htmlwidgets::saveWidget(p, "./profile_susieR_susie_rss.html")
```


From the result of line profiling on `susieR:::susie_rss` function, the most time and memory consuming part in it is `cov2cor` function. Therefore, we decided to try use other implementations to `cov2cor` functions to make it run faster. Luckily, we found an alternative implementations, `correlateR::cov2corArma()` function, may worth tying. 

In this report, we use `microbenchmark` package to compare the execution time of `correlateR::cov2corArma` and `cov2cor`.

```{r,warning=FALSE}
X=read.csv("./cov2cor.csv",header = F)
library(microbenchmark)
microbenchmark(A = correlateR::cov2corArma(as.matrix(X)),
              B = cov2cor(as.matrix(X)))

```
From the result of `microbenchmark` function, when dealing with the same matrix, the average time used in `cov2cor` is more than three times than `correlateR::cov2corArma`. Therefore, it's reasonable to replace the `cov2cor` function with `correlateR::cov2corArma` in `susieR_rss` function.

Next, we will use the same dataset used in previous to perform the line profiling and see if the optimized `susie_rss` function has a better performance. 


```{r,message=FALSE}
sourceFolder <- function(folder, recursive = FALSE, ...) 
{ 
  files <- list.files(folder, pattern = "[.][rR]$", 
                      full.names = TRUE, recursive = recursive)
  if (!length(files))
    stop(simpleError(sprintf('No R files in folder "%s"', folder)))
  src <- invisible(lapply(files, source, ...))
  message(sprintf('%s files sourced from folder "%s"', length(src), folder))
}
sourceFolder("./R/R", recursive = TRUE)
```

```{r}

p2=profvis({
  susie_rss(as.matrix(ss_qc$z),as.matrix(LD), n = 1138870,var_y, z_ld_weight = 0, estimate_residual_variance = FALSE, 
            prior_variance = 50, check_prior = TRUE, max_iter = 1000,verbose = TRUE )
})
p2
```
```{r,include=FALSE}
htmlwidgets::saveWidget(p2, "./profile_susie_rss.html")
```

From the above result, the optimized `susie_rss` spend about 1000 MB less memory and 1900 ms less time compared to original `susie_rss` function. Therefore, we believe optimized `susie_rss` has a better performance. 



